Inference methods comparison for the simplified Naomi model

### 2023-03-23 src/naomi-simple_compare/comparison.Rmd
Add stopifnot to check we have all samples from all methods. Stan failing even with latest archived run. Go back and make sure Stan is getting model outputs #24

>>>>

Check that the parameters (latent field, hyperparameters, model outputs) sampled from each of the four methods are the same:

```{r}
stopifnot(names(tmb$fit$sample) == names(aghq$quad$sample))
stopifnot(names(tmb$fit$sample) == names(adam$adam$sample))
stopifnot(names(tmb$fit$sample) == names(tmbstan$mcmc$sample))
```
